---
title: "asf prldm heterotypic analysis"
output:
  html_notebook: default
  pdf_document: default
---

```{r}
library(ggplot2)
library(dplyr)
library(here)

source(here("scripts", "roundTwo", "main.R"))
```

```{r, message = FALSE}
x030_152 <- process_data("030_152")
x030_158 <- process_data("030_158")
```

## 030_152 (old materials)

The results seem inconsistent with expectations and conditions were not using the same materials as newer replicates

```{r}
x030_152 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0 && !monomer_conc == 25) %>%
      filter(fibril_conc == 1) %>%
      filter(hours <= hours(24)) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_152 | 1 uM asf | by reaction",
           subtitle = "[figure 1a]")
x030_152 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0 && !monomer_conc == 25) %>%
      filter(fibril_conc == 2) %>%
      filter(hours <= hours(24)) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_152 | 2 uM asf | by reaction",
           subtitle = "[figure 1b]")
x030_152 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0 && !monomer_conc == 25) %>%
      filter(fibril_conc == 4) %>%
      filter(hours <= hours(24)) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_152 | 4 uM asf | by reaction",
           subtitle = "[figure 1c]")

```

## 030_158 (recent)

Some strange "bunching" between 10 and 15 uM monomer is observed at one and two uM fibrils, but not four uM fibrils.

```{r}
x030_158 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 1) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_158 | 1 uM asf | by reaction",
           subtitle = "[figure 2a]")
x030_158 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 2) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_158 | 2 uM asf | by reaction",
           subtitle = "[figure 2b]")
x030_158 %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 4) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "030_158 | 4 uM asf | by reaction",
           subtitle = "[figure 2c]")

```

```{r}
heterotypic <- bind_rows(x030_152, x030_158) %>%
      normalize_by_commonfactor()
```

## Datasets combined and normalized

It is clear that these cannot be considered replicates. More datasets with new conditions should be collected.

```{r}
heterotypic %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 1) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "both datasets | 1 uM asf | by reaction",
           subtitle = "[figure 3a]")
heterotypic %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 2) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "both datasets | 2 uM asf | by reaction",
           subtitle = "[figure 3b]")
heterotypic %>% 
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      filter(fibril_conc == 4) %>%
      filter(hours <= hours(24)) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "both datasets | 4 uM asf | by reaction",
           subtitle = "[figure 3c]")

```
