---
title: "R Notebook"
output: html_notebook
---

```{r}
library(here)
here()
# source(here("scripts", "roundTwo", "main.R"))
```

## aS monomer reactions

```{r paged.print=TRUE}
hybrid %>% 
      filter(exp == "030_156 A") %>%
      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "raw asm rxns of 030_156 A",
           subtitle = "[figure 1a]")

hybrid %>% 
      filter(exp == "030_156 B") %>%
      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "raw asm rxns of 030_156 B",
           subtitle = "[figure 1b]")

hybrid %>% 
      filter(exp == "030_157 A") %>%
      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      
      labs(title = "raw asm rxns of 030_157 A",
           subtitle = "[figure 1c]") +
      geom_line()

hybrid %>% 
      filter(exp == "030_157 B") %>%
      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      
      labs(title = "raw asm rxns of 030_157 B",
           subtitle = "[figure 1d]") +
      geom_line()

```

We got very consistent results from the hf-asm reactions. They simply need to be scaled by the correction procedure.

```{r}
hybrid %>% 
      filter(grepl("030_156", exp)) %>%

      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = exp)) +
      geom_point() +
      geom_line() +
      labs(title = "raw asm rxns of 030_156",
           subtitle = "[figure 2a]")
hybrid %>% 
      filter(grepl("030_157", exp)) %>%
      
      filter(monomer_type == "asm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = exp)) +
      geom_point() +
      geom_line() +
      labs(title = "raw asm rxns of 030_157",
           subtitle = "[figure 2b]")
```

We can see that each replicate of the asm reactions maintains relatively similar ratios, just at different scales.


```{r}
hybrid %>% 
      filter(grepl("030_156", exp)) %>%

      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = exp)) +
      geom_point() +
      geom_line() +
      labs(title = "raw prldm rxns of 030_156",
           subtitle = "[figure 3a]")
hybrid %>% 
      filter(grepl("030_157", exp)) %>%
      
      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = exp)) +
      geom_point() +
      geom_line() +
      labs(title = "raw asm rxns of 030_157",
           subtitle = "[figure 3b]")
```
It's immediately apparent that these reactions aren't making as much sense, or at least the pattern isn't as immediately clear. It's interesting in figure 3a that while the B replicate had a standard outcome for 5, 10, and 15 uM reactions, A did not. Further, both A and B had the same general reaction in their 20 uM reactions. Let's take a closer look at figure 3a.

```{r}
hybrid %>% 
      filter(exp == "030_156 A") %>%
      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "raw prldm rxns of 030_156 A",
           subtitle = "[figure 1b]")

hybrid %>% 
      filter(exp == "030_156 B") %>%
      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      geom_line() +
      labs(title = "raw prldm rxns of 030_156 B",
           subtitle = "[figure 1b]")

hybrid %>% 
      filter(exp == "030_157 A") %>%
      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      
      labs(title = "raw prldm rxns of 030_157 A",
           subtitle = "[figure 1d]") +
      geom_line()
hybrid %>% 
      filter(exp == "030_157 B") %>%
      filter(monomer_type == "prldm") %>%
      filter(!monomer_conc == 0 && !fibril_conc == 0) %>%

      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      
      labs(title = "raw prldm rxns of 030_157 B",
           subtitle = "[figure 1d]") +
      geom_line()
```


```{r}
hybrid %>% 
      filter(exp == "030_157 B") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
           color = reaction)) +
      geom_point() +
      
      labs(title = "raw rxns of 030_157 B",
           subtitle = "") +
      geom_line()

```



```{r}
hybrid %>%
      filter(!id == "2 hf 20 prldm 030_156 B") %>%
      filter(!fibril_conc == 0) %>%
      filter(!monomer_conc == 0) %>%
      
      filter(hours <= hours(24)) %>%

      filter(monomer_conc <=10) %>%
      filter(monomer_type == "asm") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
                 color = exp)) +
      # geom_errorbar(aes(
      #       ymin = value - sd, ymax = value + sd), width = 0.2) +
      geom_point() +
      
      labs(title = "uncorrected | asm | by exp",
           subtitle = "") +
      geom_line()


```

```{r}
hybrid_normalized %>%
      filter(!id == "2 hf 20 prldm 030_156 B") %>%
      filter(!fibril_conc == 0) %>%
      filter(!monomer_conc == 0) %>%
      
      filter(hours <= hours(24)) %>%

      filter(monomer_conc <=10) %>%
      filter(monomer_type == "asm") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
                 color = exp)) +
      # geom_errorbar(aes(
      #       ymin = value - sd, ymax = value + sd), width = 0.2) +
      geom_point() +
      
      labs(title = "normalized | asm | by exp",
           subtitle = "") +
      geom_line()
```

```{r}
hybrid %>%
      filter(!id == "2 hf 20 prldm 030_156 B") %>%
      filter(!fibril_conc == 0) %>%
      filter(!monomer_conc == 0) %>%
      
      filter(hours <= hours(24)) %>%

      filter(monomer_type == "asm") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
                 color = reaction)) +
      # geom_errorbar(aes(
      #       ymin = value - sd, ymax = value + sd), width = 0.2) +
      geom_point() +
      
      labs(title = "uncorrected | asm | by reaction",
           subtitle = "") +
      geom_line()

```

```{r}
hybrid_normalized %>%
      filter(!id == "2 hf 20 prldm 030_156 B") %>%
      filter(!fibril_conc == 0) %>%
      filter(!monomer_conc == 0) %>%
      
      filter(hours <= hours(24)) %>%

      filter(monomer_type == "asm") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
                 color = reaction)) +
      # geom_errorbar(aes(
      #       ymin = value - sd, ymax = value + sd), width = 0.2) +
      geom_point() +
      
      labs(title = "normalized | asm | by reaction",
           subtitle = "") +
      geom_line()

```

```{r}
hybrid_normalized_stats %>%
      filter(!id == "2 hf 20 prldm 030_156 B") %>%
      filter(!fibril_conc == 0) %>%
      filter(!monomer_conc == 0) %>%
      
      filter(hours <= hours(24)) %>%

      filter(monomer_type == "asm") %>%
      
      ggplot(aes(x = hours / 3600, y = value, group = id,
                 color = reaction)) +
      # geom_errorbar(aes(
      #       ymin = value - sd, ymax = value + sd), width = 0.2) +
      geom_point() +
      
      labs(title = "normalized | asm | by reaction",
           subtitle = "") +
      geom_line()

```
